Verification of the CVM algorithm

### 2025-03-04 isabelle/CVM_Transforms/document/root.tex
wording
slight fixes

  This project formalises the new, corrected proof of the CVM algorithm, while
  strengthening the correctness result of Theorem 2 in \cite{cvm_2023} to provide
  the same correctness guarantee using a smaller threshold
  (and hence space usage) of
  $\lceil \frac{12}{\varepsilon^2} \text{log}_2 \frac{3m}{\delta} \rceil$,
  where $m$ is the length of the input stream.

  This corrected proof performs a sequence of transformations of the CVM
  algorithm, akin to cryptographic game-hopping.
  The reason for these transformations is that standard techniques for analysing
  randomised algorithms such as the Chernoff bounds usually require independence
  of state random variables, which is unfortunately absent from the CVM
  algorithm, but was incorrecty claimed and used in the original proof.
  The transformations address this by successively simplifying the
  algorithm into one where the state variables are independent, enabling
  the use of the Chernoff bounds.

@@

    \item Strong forms of the multiplicative Chernoff bounds for the binomial
    distribution, derived from the Bennet-Bernstein inequalities.
  \end{enumerate}
\end{abstract}

>>>>

  This project formalises the new, corrected proof of the CVM algorithm, while
  strengthening the correctness result of Theorem 2 in \cite{cvm_2023} to provide
  the same correctness guarantee using a slightly smaller threshold
  (and hence space usage) of
  $\lceil \frac{12}{\varepsilon^2} \text{log}_2 \frac{3m}{\delta} \rceil$,
  where $m$ is the length of the input stream.

  This proof performs a sequence of transformations from the CVM algorithm,
  akin to cryptographic game-hopping.  The reason for these transformations is
  that standard techniques for analysing randomised algorithms such as the
  Chernoff bounds usually require independence of state random variables, which
  is unfortunately absent from the CVM algorithm.  The transformations address
  this by successively simplifying the algorithm into one where the state
  variables are independent, enabling the use of the Chernoff bounds.

@@

    \item Strong forms of the multiplicative Chernoff bounds for the binomial
    distribution, derived from the Bennett-Bernstein inequalities.
  \end{enumerate}
\end{abstract}
